Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-25 tex/results.tex
not really satisfied
fix part about mesh densities

\subsubsection{Grid-independence study}

We performed a grid-independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the $z$-axis (a similar setup to the square cylinder on Fig. 18 of 
Rockstuhl et al.\cite{rockstuhl2005}). 
Due to the nature of the geometry and its sharp edges, it was challenging to see proper convergence. 
We have completed grid-convergence analysis for this type of physics in a previous work, but using spherical geometries \cite{ClementiETal2019}. 
With that experience, and given the difficulty caused by sharp edges, we are satisfied with studying grid-independence here instead.
Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 triangles (density $9.05\times10^{-4}$ per $\text{\AA}$ squared)
 to 19,200 triangles (density $1.11\times10^{-5}$ $\text{\AA}$ squared):
 the computed results show no discernible difference.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{cubeL535nm_15Kvs19K.pdf} 
    \caption{Grid-independence study for a SiC cube of side $L=535 nm$ submerged in air under a constant 
    electric field in the $z$-direction. The curves represent the extinction cross-section divided by $L^2$ 
    as a function of wavelength divided by $L$.}
    \label{fig:cube535}
 \end{figure}

@@

Based on the results of our grid-independence study, we decided to use triangle densities in the order of $6$ to $9\times10^{-5}$
to produce the meshes for the replication of figures 14a and 14b in the work of Rockstuhl et al.\ (case $a1=672$, $b=328$). For the third 
dimension, we needed to choose a value that represents ``infinity.'' To achieve this, we studied the effects of 
elongating the cylinder to the third dimension. In Figure \ref{fig:ext_y_14}, we present the results for two different
values of the length in the third dimension, $y=1344$ nm ($2\times a$) and $y=2688$ nm ($4\times a$). We see that as we make $y$ longer, the 
intensity of some peaks decreases, due to the fact that some of the peaks are associated to this component. Therefore, 
from now on we use $y=2688$ nm. We could have increased this value more, but the
simulations then become computationally more expensive and we would still have the 3D effects in the model.

>>>>

\subsubsection{Grid-independence study}\label{sec:independence}

We performed a grid-independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the $z$-axis (a similar setup to the square cylinder on Fig. 18 of 
Rockstuhl et al.\cite{rockstuhl2005}). 
Due to the nature of the geometry and its sharp edges, it was challenging to see proper convergence. 
We have completed grid-convergence analysis for this type of physics in a previous work, but using spherical geometries \cite{ClementiETal2019}. 
With that experience, and given the difficulty caused by sharp edges, we are content with studying grid-independence here instead.
Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 triangles (density $9.05\times10^{-4}$ per $\text{\AA}$ squared)
 to 19,200 triangles (density $1.11\times10^{-5}$ $\text{\AA}$ squared):
 the computed results show no discernible difference.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{cubeL535nm_15Kvs19K.pdf} 
    \caption{Grid-independence study for a SiC cube of side $L=535$ nm submerged in air under a constant 
    electric field in the $z$-direction. The curves represent the extinction cross-section divided by $L^2$ 
    as a function of wavelength divided by $L$.}
    \label{fig:cube535}
 \end{figure}

@@

The constraints of mesh generation mean that we have only loose control on triangle density. Our meshes for the rectangular prism all have densities like in the coarse case of the grid-dependence study of section \ref{sec:independence}, or finer.
For the third dimension, we needed to choose a value that represents ``infinity.'' To achieve this, we studied the effects of 
elongating the cylinder to the third dimension. In Figure \ref{fig:ext_y_14}, we present the results for two different
values of the length in the third dimension, $y=1344$ nm ($2\times a$) and $y=2688$ nm ($4\times a$). We see that as we make $y$ longer, the 
intensity of some peaks decreases, due to the fact that some of the peaks are associated to this component. Therefore, 
from now on we use $y=2688$ nm. We could have increased this value more, but the
simulations then become computationally more expensive and we would still have the 3D effects in the model.
